######Title: A Simulation Exercise for Exponential Distribution and Central Limit Theorem
######Author: Thomas Ng Jia Chee
######Date: 20 October 2015

## Overview

This simulation aims to investigate the exponential distribution in R and compare it with Central Limit Theorem. The exponential distribution is the probability distribution that describes the time between events in a Poisson process. 

**Mean = Standard Deviation = lambda^(-1)**

Central Limit Theorem states that, when sufficient large number of iterates of independent random variables, the result will be approximately normally distributed, regardless of the underlying distribution. 

**In this simulation lambda is set at *0.2*, sample size is *40* and number of simulation (sampling) is *1000*.**

## Simulation

```{r}
# set lambda 
lambda <- 0.2

# set number of observation (sample size)
n <- 40

# set number of simualtion (sampling)
count <- 1000

# simulate exponential distribution of 'n' samples a 'count' times
exp_dist_simulation <- replicate(count, rexp(n, lambda))

# apply function 'mean' to 'exp_dist_simulation', 2 represents column
# also called Sampling Distribution of the Sample Mean
sample_mean <- apply(exp_dist_simulation, 2, mean)
```

## Result of simulation 

In theory, both mean and standard deviation of this expoenential distribution simulation should be *1/lambda (0.2)* which is *5*. 

Standard Error (standard deviation of the sampling distribution of the sample mean) is standard deviation of the population divides by the square root of number of observation, *5/sqrt(1000)* which is *0.79*. 

Let's find out if simulation result matches theory.
```{r}
# mean of Sampling Distribution of the Sample Mean (mean of means)
# is it 5 ?
mean(sample_mean)
# standard deviation of Sampling Distribution of the Sample Mean
# aka Standard Error
# is it 0.79 ?
sd(sample_mean)
# variance, is it 0.62 (0.79^2) ?
var(sample_mean)
```

Central limit theorem states that the result would be normally distributed.
```{r simpleplot}
# is it normally distributed ?
hist(sample_mean, breaks=40)
```

**In conclusion, this simulation supports central limit theorem. The simulation results are significantly close to theoretical mean and variance. In addition, the sampling distribution is normally distributed, regardless of the underlying distribution.**

