-----
Title: Central Limit Theorem - A Simulation Exercise
Author: Thomas Ng Jia Chee
Date: 20 October 2015


-----
## Overview

This simulation aims to investigate the exponential distribution in R and compare it with Central Limit Theorem. The exponential distribution is the probability distribution that describes the time between events in a Poisson process. 

**Mean = Standard Deviation = lambda^(-1)**

Central Limit Theorem states that, when sufficient large number of iterates of independent random variables, the result will be approximately normally distributed, regardless of the underlying distribution. 

In this simulation lambda is set at *0.2*, sample size is *40* and number of simulation (sampling) is *1000*.

-----
## Simulation

```{r}
#set lambda 
lambda <- 0.2

#set number of observation (sample size)
n <- 40

#set number of simualtion (sampling)
count <- 1000

#simulate exponential distribution of 'n' samples a 'count' times
exp_dist_simulation <- replicate(count, rexp(n, lambda))

#apple function 'mean' onto 'exp_dist_simulation', 2 represents column
#also called Sampling Distribution of the Sample Mean
sample_mean <- apply(exp_dist_simulation, 2, mean)
```


## Result of simulation

In theory, both mean and standard deviation of this expoenential distribution simulation should be *1/lambda (0.2)* which is *5*. Variance is square of standard deviation. Thus, it should be *25*. 

Let's find out if simulation result matches theory.
```{r}
# mean of Sampling Distribution of the Sample Mean (mean of means)
mean(sample_mean)
var(sample_mean)
```

Here, it is proven that simulation result is significantly close to theoretical mean and variance.