#####Title: **Analyze the ToothGrowth data in the R datasets package**
#####Author: **Thomas NG Jia Chee**
#####Date: **20 October 2015**

##Overview

This project analyzes the ToothGrowth data in the R datasets package. It consists of 3 parts:

1. A basic summary of the data
2. Confidence intervals and hypothesis tests to compare tooth growth by **supplement type** and **quantity of dose**
3. Conclusions and the assumptions taken

---

##1. A Basic Summary of Tooth Growth data

```{r}
# load dataset
library(datasets)
data("ToothGrowth")

# structure of dataset
str(ToothGrowth)
# summary of dataset
summary(ToothGrowth)
# explore data using graphical method, using ggplot2
library(ggplot2)
# a quick plot to compare supplement type & quantity of dose
qplot(supp, len, data=ToothGrowth, geom=c('boxplot'), fill=as.factor(dose))
```

The observation from the graph is

1. **Supplement type does not have strong correlation with tooth growth.**
2. **Higher amount of supplement dose may stimulate tooth growth.**

---

##2. Confidence intervals and hypothesis tests

####Part 2.1: The correlation between supplement type and tooth growth

>Null hypothesis states that supplement has no significant difference in stimulating tooth growth. T-test is conducted at 5% significance level.
```{r}
# use t-test to compare tooth growth by supplement type
t.test(len ~ supp, data = ToothGrowth)
```

T-test shown that, at 95 percent confience interval,

1. P-value is 6%, higher than 5%.
2. Confidence interval contains 0

**Thus, null hypothesis CANNOT be rejected. Supplement type does not have strong correlation with tooth growth.**

---

####Part 2.2: The correlation between quantity of dose and tooth growth

>Null hypothesis states that quantity of dose has no significant difference in stimulating tooth growth. T-test is conducted at 5% significance level. 
```{r}
# To determine correlation of quantity of dose with tooth growth, subset groups based on dose levels, using package 'dplyr'
# There 3 groups (3 Choose 2):
library(dplyr)
group_one <- filter(ToothGrowth, dose %in% c(0.5,1))
group_two <- filter(ToothGrowth, dose %in% c(0.5,2))
group_three <- filter(ToothGrowth, dose %in% c(1,2))

# conduct t-test for all groups
t.test(len ~ dose, data=group_one)
t.test(len ~ dose, data=group_two)
t.test(len ~ dose, data=group_three)

```

All of the t-test above shown that, at 95 percent confience interval,

1. P-value is significantly less than 5%
2. Confidence interval is well above 0

**Thus, null hypothesis CAN be rejected. Higher quantity of dose stimulates tooth growth.**

---

##3. Conclusions and assumptions taken

In conclusion,

1. Supplement type does not have strong correlation with tooth growth.
2. Higher quantity of dose stimulates tooth growth.

The conclusions drawn from above t-test are based on the following assumptions,

* Bivariate independent variable (A, B groups)
* Continuous dependent variable
* Each observation of the dependent variable is independent of the other observations of the dependent variable (its probability distribution isn't affected by their values).

Source: http://www.csic.cornell.edu/Elrod/t-test/t-test-assumptions.html